% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
urlcolor=black
}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Aslam Tajwala}  & 408-316-1679\\
93 Bettencourt Way, &  atajwala@gmail.com\\
Milpitas, CA 95035. & \url{http://www.aslamtajwala.com}\\
& \url{https://www.github.com/atajwala}\\
%& http://www.linkedin.com/in/atajwala\\
\end{tabular*}
\\

\vspace{0.1in}



\resheading{Skills}

\begin{description}
\item[Programming Languages:]
Ruby, C/C++, Java

\item[Web stack:]
Rails 3.x, JavaScript, CSS3, HTML5, Ajax, JSON, XML 

\item[Databases:]
MySQL, NoSQL (MongoDB)

\item[Dabbled with:]
JQuery, Passenger, Mongrel, Content caching (Memcache)

\item[Source control:]
Git, SVN, CVS

\item[Environments:]
Unix/Linux, Amazon Web Services, Heroku, Mac OSX, Solaris

\item[Scripting:]
Unix shell, Applescript, Tcl/Expect

\item[Other:]
OpenSSL, HTTP, Flash, GDB, TCP/IP, Ethereal/TcpDump

\end{description}

\resheading{Work Experience}
\begin{itemize}

\item
	\ressubheading{TweetsAround (\url{http://tweetsaround.com})}{Self contributer}{Web Programmer}{Oct. 2011 - Present}
	\begin{itemize}
		\resitem{Developed a Rails application that demonstrates mashing of MongoDB, Twitter API and Google Maps API.}
		\resitem{Using the Twitter Streaming API this web-app lists tweets near a geographical location specified by the user.}
		\resitem{A separate task continuously populates tweets to a database thats geo-spatially indexed. 
		 		 Making the application more responsive and robust.}
		\resitem{Uses: Rails 3.1, Mongoid gem.  Deployed on Heroku (1 web dyno and 1 worker dyno). Database hosted via MongoHQ.}
		\resitem{Ajax based UI using JQuery. Supports all well known browsers.}
	\end{itemize}

\item
	\ressubheading{Mail2share (\url{http://mail2share.com})}{Self contributer}{Web Programmer}{Jan. 2011 - Present}
	\begin{itemize}
		\resitem{Developed a RESTful Rails webapp to test the need for a social inbox.}
		\resitem{Wrote the backend, TDD for MVC modules, handcrafted most of the UI.}
		\resitem{Used Authlogic for authentication, Sphinx for search, Postfix for mailserver.}
		\resitem{Deployed on AWS. Runs on - Apache, Phusion Passenger and Mongrel.}
		\resitem{Performed basic profiling and optimizations.}
		\resitem{This is a work still under progress.}
	\end{itemize}
		
\item
	\ressubheading{Juniper Networks Inc.}{Sunnyvale, CA}{Software Engineer}{July 2006 - Present}
	\begin{itemize}
		\resitem{Developed software for the JUNOS operating system in the areas of virtual 
		         private networks (VPN), application layer gateways (ALG), and firewall subsystem.}
		\resitem{Worked on an array of platforms; from high to low performance Juniper gateways - 
				 with a variety of architectures such as multi-chassis, multi-core, multi-threaded 
				 BSD-Unix environments with high-availability and fail-over capabilities.}
		\resitem{Profiling and optimizing a suite of cryptographic algorithms.}
	\end{itemize}

\item 
	\ressubheading{Aspect Labs}{Santa Clara, CA}{Security Engineer}{Aug. 2005 - May 2006}
	\begin{itemize}
		\resitem{Implemented an encryption library for handheld 3G devices.}
		\resitem{Developed an in-house cryptographic suite that allowed certification of various 
				 security products.}
		\resitem{Contributed towards certifying access-control-lists and privileges for the 
				 Solaris-10 OS, extensively making use of RSAs PKCS11 cryptographic library.}
	\end{itemize}

\item
	\ressubheading{Suyoga Technologies}{Bangalore, India}{Web programmer}{Jan. 2004 - July 2004}
	\begin{itemize}
		\resitem{Responsible for complete life-cycle of a network monitoring webapp (browser+mobile) 
				 for network administration.}
		\resitem{The product was used by network administrators and allowed them to monitor network 
				 health via any WAP enabled mobile phone.} 
	\end{itemize}
	
\end{itemize}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Northwestern Polytechnic University}{Fremont, CA}{Master of Science - Computer Science (GPA 3.97)}{2006-2007}
%	\begin{itemize}
%		\resitem{Relevant courses: }
%	\end{itemize}

\item
	\ressubheading{Rochester Institute of Technology}{Rochester, NY}{Master of Science - Computer Science (GPA 3.5)}{2004-2006}
%	\begin{itemize}
%		\resitem{Relevant courses: Advanced Java programming, }
%	\end{itemize}
	
\item
	\ressubheading{H.K.B.K. College of Engineering}{Bangalore, India}{Bachelor of Science - Computer Science (GPA 3.5)}{2000-2004}
%	\begin{itemize}
%		\resitem{Relevant courses: }
%	\end{itemize}

\end{itemize}

\resheading{Academic Projects}
\begin{itemize}

\item
	\ressubheading{"Distributed Reflective Denial Of Service" attack}{Fremont, CA}{Academic Project}{2007}
	\begin{itemize}
		\resitem{Implemented an attack engine that in coordination with other zombie hosts performed 
				 a simultaneous bandwidth attack.}
		\resitem{Elegant multi-threaded/load-balanced design for the DOS attack. Implemented various 
				 traffic patterns to by-pass naive Firewalls/IDS systems and report back with statistical 
				 information.}
	\end{itemize}
	
\item
	\ressubheading{"Routing and Security" for an Ad Hoc Network}{Rochester, NY}{Academic Project}{2006}
	\begin{itemize}
		\resitem{Implemented a dynamic source routing algorithm and made significant enhancements to it.}
		\resitem{Coordinated team efforts to provide mobile node authentication with TESLA.}
	\end{itemize}

\item
	\ressubheading{Watermarking of Relational Databases}{Rochester, NY}{Academic Project}{2005}
	\begin{itemize}
		\resitem{Designed and implemented in a team project using PERL, Java, OracleDB on Solaris.}
		\resitem{Implemented features such as verification of ownership, non-repudiation of database, and rollback.}
	\end{itemize}

\item
	\ressubheading{A cross-platform Chat application}{Rochester, NY}{Academic Project}{2004}
	\begin{itemize}
		\resitem{Implemented features such as group chat, buddy chat, session management in Java, C++.}
		\resitem{Profiled/fine-tuned the chat engine to provide faster and robust concurrency among clients.}
	\end{itemize}
				
\end{itemize}


\resheading{Interests}

\begin{description}
\item[Internet:] consumer/enterprise webapps.
\item[Other:] volunteering, reading, hiking, swimming.
\end{description}

\end{document}
